---
title: "Make a request"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Make a request}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sora)
```

## Example: make a request

Several linking are possible using SoRa. This is a basic example which shows you how to solve a common problem.
First, make sure you attach the `sora` package to the session. For this example, we use the synthetic `ber_income` dataset.
See `?ber_income` for details.

```{r}
head(ber_income)
```

Before you actually send requests, make sure to have an SoRa API key `vignette("Get SoRa API key", package = "sora")`.
You will only be able to use data that you signed the necessary usage agreements for. To see whether the API is available and your key is
valid, you can run `sora_available()`. If it returns `TRUE`, you are good to go.

``` r
sora_available()
```

SoRa accepts three types of survey datasets. You can either provide the IDs of dataset provided by SoRa, provide your own datasets, or use
identifiers of administrative areas in Germany (e.g., zip codes or municipality keys). For our dummy example, we use `sora_custom` to
signal that we use our own data.