---
title: "Get SoRa API key"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get SoRa API key}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sora)
```

## Get SoRa API key 

Before you can use the SoRa API you need an `SoRa API Key`. The key you can get [here](https://sora.gesis.org/unofficial/sora-user-mod/users/request-api-key).

You will have to proved some personal information and, importantly,
agree to the mandatory and optional agreements. Optional agreements are
made with the service providers and are the requirement to use their
service. For example, if you do not agree to the user agreement of the
IOER, then you will not be able to use their services within SoRa.

Please ensure that you never publish your API key to the public in plain
text. This also includes uploads of any kind, e.g., to GitHub. The
package functions feature an `api_key` argument, but you are advised to
never use it. Instead, we suggest to use one of the following options:

- Set an environment variable `SORA_API_KEY` in your `.Renviron` file
  (see [here](https://docs.posit.co/ide/user/ide/guide/environments/r/managing-r.html#renviron)
  to learn more about `.Renviron` files)
- Pass `api_key = "ask"` to any SoRa function. This will open up a
  masked prompt where you can enter your API key safely. You must only
  do this once per session.